A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-24 manuscript.Rmd
Revert "add missing backtick"
This reverts commit 1a3ddd3a3960909c8b5e8f9ce641fbef61763c31.
add missing backtick

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output:
  bookdown::pdf_document2:
    keep_tex: true
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---
